DeepSphere: a graph-based spherical CNN

### 2019-11-15 main.tex
small updates

\paragraph{Theoretical convergence.}
We extend the work of \citep{belkin2005towards} to a sufficiently regular, deterministic sampling.
Following their setting, we will work with the extended graph Laplacian operator as the linear operator $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ such that
\begin{equation} \label{eq:Heat Kernel Graph Laplacian operator}
	 L_n^t f(y) := \frac{1}{n}\sum_{i=1}^{n} e^{ -\frac{\|x_i-y\|^2}{4t}} \left(f(y)-f(x_i)\right).
\end{equation}
This operator extends the graph Laplacian operator previously defined with the weighting scheme \eqnref{weights:belkin} to each point of the manifold, i.e., the sphere.
\mdeff{Can we avoid to introduce general manifolds and stay on the sphere?}
As the radius of the kernel $t$ will be adapted to the number of samples, we also rescale the graph Laplacian operator as $\hat{L}_n^t := \frac{|\mathbb S^2|}{4\pi t^2}L_n^t$.
Hence, we have $\b{L}_n^t \b{f} = T_\V L_n^t f$.
% $\b{\hat L} = \frac{|\mathbb S^2|}{4\pi t^2}\b L_n^t$. \nati{why define this, we are not using it}
Given a sampling $\V$, we define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, $A_i$ its corresponding area, and $d_i$ the largest distance between the center $x_i$ and any point on the surface $\sigma_i$.
Define $d^{(n)} := \max_{i=1, \dots, n} d_i$ and $A^{(n)} := \max_{i=1, \dots, n} A_i$.
%Given any rotation $g\in SO(3)$, we define the corresponding rotation operator $\mathcal R_g$ such that for any function $f$ on the sphere
%\mdeff{Already defined in problem formulation.}
%\begin{equation} \label{eq:rotation operator}
%	\mathcal R_g f(x) := f(g^{-1}(x)).
%\end{equation}
\begin{theorem}
	For a sampling $\V$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{n^\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$, for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance in $\R^3$, for all $y\in\S^2$, there exists a sequence $t_n = n^\beta$, $\beta\in\mathbb R$ such that
% 	the rescaled Heat Kernel Graph Laplacian $\frac{|\S^2|}{4\pi t_n^2}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\S^2}$
	\begin{equation*}
		\lim_{n\to\infty}\hat{L}_n^{t_n}f(y) = \triangle_{\S^2}f(y).
	\end{equation*}
	\label{theo:pointwise convergence for a regular sampling}
\end{theorem}
As a direct implication of this theorem, the discrete counterpart of $\mathbf{\hat L}$ \mdeff{(that's already discrete no?)} converges pointwise towards the Laplace-Beltrami operator $\Delta_{\S^2}$ in the sense explained in \citep{belkin2007convergence}.
This operator commutes with rotation and hence Theorem \ref{theo:pointwise convergence for a regular sampling} is a strong step towards equivariance. We formalize it in the following theorem.
\mdeff{This transition should be done better.}
\begin{theorem}\label{theo:equivariance}
Under the hypothesis of theorem~\ref{theo:pointwise convergence for a regular sampling}, the rescaled graph Laplacian commutes with any rotation, in the limit of infinite sampling, i.e.,
\begin{equation*}
	\forall y\in\mathbb S^2\quad\left| \mathcal R_g \hat L_n^{t_n} f (y) - \hat L_n^{t_n} \mathcal R_g f(y) \right| \xrightarrow{n\to\infty}0.
\end{equation*}
\end{theorem}

>>>>

\paragraph{Theoretical convergence.}
We extend the work of \citep{belkin2005towards} to a sufficiently regular, deterministic sampling.
Following their setting, we will work with the extended graph Laplacian operator as the linear operator $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ such that
\begin{equation} \label{eq:Heat Kernel Graph Laplacian operator}
	 L_n^t f(y) := \frac{1}{n}\sum_{i=1}^{n} e^{ -\frac{\|x_i-y\|^2}{4t}} \left(f(y)-f(x_i)\right).
\end{equation}
This operator extends the graph Laplacian operator previously defined with the weighting scheme \eqnref{weights:belkin} to each point of the the sphere.
% \mdeff{Can we avoid to introduce general manifolds and stay on the sphere?} \nati{yes}
As the radius of the kernel $t$ will be adapted to the number of samples, we also rescale the graph Laplacian operator as $\hat{L}_n^t := \frac{|\mathbb S^2|}{4\pi t^2}L_n^t$.
Hence, we have $\b{L}_n^t \b{f} = T_\V L_n^t f$.
% $\b{\hat L} = \frac{|\mathbb S^2|}{4\pi t^2}\b L_n^t$. \nati{why define this, we are not using it}
Given a sampling $\V$, we define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, $A_i$ its corresponding area, and $d_i$ the largest distance between the center $x_i$ and any point on the surface $\sigma_i$.
Define $d^{(n)} := \max_{i=1, \dots, n} d_i$ and $A^{(n)} := \max_{i=1, \dots, n} A_i$.
%Given any rotation $g\in SO(3)$, we define the corresponding rotation operator $\mathcal R_g$ such that for any function $f$ on the sphere
%\mdeff{Already defined in problem formulation.}
%\begin{equation} \label{eq:rotation operator}
%	\mathcal R_g f(x) := f(g^{-1}(x)).
%\end{equation}
\begin{theorem}
	For a sampling $\V$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{n^\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$, for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance in $\R^3$, for all $y\in\S^2$, there exists a sequence $t_n = n^\beta$, $\beta\in\mathbb R$ such that
% 	the rescaled Heat Kernel Graph Laplacian $\frac{|\S^2|}{4\pi t_n^2}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\S^2}$
	\begin{equation*}
		\lim_{n\to\infty}\hat{L}_n^{t_n}f(y) = \triangle_{\S^2}f(y).
	\end{equation*}
	\label{theo:pointwise convergence for a regular sampling}
\end{theorem}
As a direct implication of this theorem, $\hat L$, the continuous rescaled counterpart of $\mathbf{L}$, 
% \mdeff{(that's already discrete no?)} \nati{good catch, fixed}
converges pointwise towards the Laplace-Beltrami operator $\Delta_{\S^2}$ in the sense explained in \citep{belkin2007convergence}.
This is a major step towards equivariance as the Laplace-Beltrami operator does commute with rotation. Based on this property, we show that the graph Laplacian is equivariant to rotation in the limit of infinite sampling.
% \mdeff{This transition should be done better.} \nati{Done}
\begin{theorem}\label{theo:equivariance}
Under the hypothesis of theorem~\ref{theo:pointwise convergence for a regular sampling}, the rescaled graph Laplacian commutes with any rotation, in the limit of infinite sampling, i.e.,
\begin{equation*}
	\forall y\in\mathbb S^2\quad\left| \mathcal R_g \hat L_n^{t_n} f (y) - \hat L_n^{t_n} \mathcal R_g f(y) \right| \xrightarrow{n\to\infty}0.
\end{equation*}
\end{theorem}
